SHARP II: Dark Matter Substructure, Gravitational Lens flux-ratio Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on Disks

### 2015-08-17 papers/B1555_EdgeOn/B1555_letter.tex
change to save space and new mnras template

\documentclass[useAMS,usenatbib]{mn2e}
%\documentclass[usenatbib]{mn2e}
\usepackage{graphicx}
%\usepackage[nottoc]{tocbibind}
\setlength{\topmargin}{-1.2cm}

@@

% Journal definitions
\newcommand{\apj}[1]{ApJ}
\newcommand{\mnras}[1]{MNRAS}
\newcommand{\apjl}[1]{ApJL}
\newcommand{\pasj}[1]{PASJ}
\newcommand{\aj}[1]{AJ}
\newcommand{\nat}[1]{Nature}
\newcommand{\aap}{A\&A}

@@

It was first suggested by \citet{Mao1998} that flux-ratio anomalies
observed in radio-loud multiple images of lensed quasars could be
interpreted as a telltale sign of the presence of substructure in lens
galaxies.  Indeed, small perturbations in the gravitational potential
are sufficient to cause flux-ratio anomalies in strong lensed systems
\citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
radio band, lensed images are neither sensitive to microlensing from
stars, nor to dust extinction. This makes flux-ratio anomalies a promising
tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002,N13}.  
%At present, the amount of substructure derived from flux-ratio anomalies
%seems to be disagreement with predictions from numerical simulations, 
%with the former requiring a larger fraction of mass in substructure than
%expected \citep{Xu14}. 
\textbf{At present, the amount of substructure derived from flux-ratio anomalies ease the disagremeent with direct-detections and numerical simulations.
Utilizing the surface brightness distribution of extended arcs and Einstein rings
has been introduced by \citet{K05} and \citet{V09}. The fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a,V12}, although the simulation results show less level of flux anomalies than expected \citep{Xu14}.}
While this could be the result of small sample
statistics, it could also be an indication that flux-ratio anomalies
have a different origin than substructure. \textbf{ISM and microlensing both can produce flux anomalies in lens systems, but the effects from ISM show strong frequency dependence and observing in radio band can avoid microlensing from star-size objects \citep{KD04}. These origins are ruled out among known radio loud flux anomlous systems support the detection of substructures. }[OTHER POSSIBLE ORIGONS--SIMONA]
%

@@

\begin{table*}
\centering
 \begin{minipage}{140mm}
  \caption{Radio observation \citep{Marlow99} and model-predicted lensed image positions (in arcsec).}
  \begin{tabular}{@{}ccccccc}
\hline

Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{2}{c}{Model} \\
					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} 	\\
					 &East &North &East 		&North \\ 
\hline
A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   \\  
B ........ &$-0.0726\pm 0.001$ 	&$+0.0480 \pm 0.001$	&$-0.0727$ &$+0.0477$  \\  
C ........ &$-0.4117\pm 0.001$  &$-0.0280 \pm 0.001$	&$-0.4117$ &$-0.0281$   \\  
D ........ &$-0.1619\pm 0.006$  &$-0.3680\pm 0.006$	&$-0.1630$ &$-0.3653$  \\  
\hline
\end{tabular}

\end{minipage}
\medskip
\end{table*}

>>>>

%\documentclass[useAMS,usenatbib]{mn2e}
\documentclass[useAMS,usenatbib]{mnras}
%\documentclass[usenatbib]{mn2e}
\usepackage{graphicx}
%\usepackage[nottoc]{tocbibind}
\setlength{\topmargin}{-1.2cm}

@@

% Journal definitions
%\newcommand{\apj}[1]{ApJ}
%\newcommand{\mnras}[1]{MNRAS}
%\newcommand{\apjl}[1]{ApJL}
%\newcommand{\pasj}[1]{PASJ}
%\newcommand{\aj}[1]{AJ}
%\newcommand{\nat}[1]{Nature}
%\newcommand{\aap}{A\&A}

@@

It was first suggested by \citet{Mao1998} that flux-ratio anomalies
observed in radio-loud multiple images of lensed quasars could be
interpreted as a telltale sign of the presence of substructure in lens
galaxies.  Indeed, small perturbations in the gravitational potential
are sufficient to cause flux-ratio anomalies in strong lensed systems
\citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
radio band, lensed images are neither sensitive to microlensing from
stars, nor to dust extinction. This makes flux-ratio anomalies a promising
tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002,N13}.  
%At present, the amount of substructure derived from flux-ratio anomalies
%seems to be disagreement with predictions from numerical simulations, 
%with the former requiring a larger fraction of mass in substructure than
%expected \citep{Xu14}. 
\textbf{At present, the amount of substructure derived from flux-ratio anomalies ease the disagremeent with direct-detections and numerical simulations.
Utilizing the surface brightness distribution of extended arcs and Einstein rings
has been introduced by \citet{K05} and \citet{V09}, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a,V12}, although the simulation results show less level of flux anomalies than expected \citep{Xu14}.}
While this could be the result of small sample
statistics, it could also be an indication that flux-ratio anomalies
have a different origin than substructure. \textbf{ISM and microlensing both can produce flux anomalies in stong lens systems, but the effects from ISM show strong frequency dependence and observing in radio band can avoid microlensing from star-size objects \citep{KD04}. These alternative origins are ruled out among known radio loud flux anomlous systems support the detection of substructures. }[OTHER POSSIBLE ORIGONS--SIMONA]
%

@@

%\begin{table*}
\begin{table}
\centering
 %\begin{minipage}{140mm}
  \caption{Radio observation \citep{Marlow99} and model-predicted lensed image positions (in arcsec). Uncertainties in position measurements are $0.001^ {\prime \prime}$ expect image D with larger uncertainty ($0.006^ {\prime \prime}$).}
  \begin{tabular}{@{}ccccc}
\hline

Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{2}{c}{Model} \\
					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} 	\\
					 &East &North &East 		&North \\ 
\hline
A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   \\  
B ........ &$-0.0726$ 	&$+0.0480 $	&$-0.0727$ &$+0.0477$  \\  
C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0281$   \\  
D ........ &$-0.1619$  &$-0.3680$	&$-0.1630$ &$-0.3653$  \\  
%A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   \\  
%B ........ &$-0.0726\pm 0.001$ 	&$+0.0480 \pm 0.001$	&$-0.0727$ &$+0.0477$  \\  
%C ........ &$-0.4117\pm 0.001$  &$-0.0280 \pm 0.001$	&$-0.4117$ &$-0.0281$   \\  
%D ........ &$-0.1619\pm 0.006$  &$-0.3680\pm 0.006$	&$-0.1630$ &$-0.3653$  \\  
\hline
\end{tabular}

%\end{minipage}
%\medskip
\end{table}
%\end{table*}
